### 2021-05-04 content/80.formal-definition.tex
bibliography

An `RO-Crate(R)` is defined as a self-described _Root Data Entity_, which describes and contains parts (_data entities_), which are further described in _contextual entities_.  These terms align with their use in the [RO-Crate 1.1 terminology](https://www.researchobject.org/ro-crate/1.1-DRAFT/terminology).

The `Root(r)` is a type of Dataset(r), and must have the metadata to literal attributes to provide a name, description and datePublished, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 [requirements for the root data entity](https://www.researchobject.org/ro-crate/1.1-DRAFT/root-data-entity.html#direct-properties-of-the-root-data-entity).

@@

The below is an example RO-Crate represented using the above formalization, assuming a base URI of [http://example.com/ro/123/](http://example.com/ro/123/):

@@

In reality many additional attributes from schema.org types like [http://schema.org/Dataset](http://schema.org/Dataset) and [http://schema.org/CreativeWork](http://schema.org/CreativeWork)  would be used to further describe the RO-Crate and its entities, but as these are optional they do not form part of this formalization.

@@

Combining the above predicates and schema.org mapping with rudimentary JSON templates, these forward-chaining production rules can output JSON-LD according to the RO-Crate 1.1 specification:

>>>>

An `RO-Crate(R)` is defined as a self-described _Root Data Entity_, which describes and contains parts (_data entities_), which are further described in _contextual entities_.  These terms align with their use in the [RO-Crate 1.1 terminology](https://www.researchobject.org/ro-crate/1.1/terminology).

The `Root(r)` is a type of Dataset(r), and must have the metadata to literal attributes to provide a name, description and datePublished, as well as a contextual entity identifying its license. These predicates correspond to the RO-Crate 1.1 [requirements for the root data entity](https://www.researchobject.org/ro-crate/1.1/root-data-entity.html#direct-properties-of-the-root-data-entity).

@@

The below is an example RO-Crate represented using the above formalization, assuming a base URI of `http://example.com/ro/123/`:

@@

In reality many additional attributes from schema.org types like <http://schema.org/Dataset> and <http://schema.org/CreativeWork> would be used to further describe the RO-Crate and its entities, but as these are optional they do not form part of this formalization.

@@

Combining the above predicates and schema.org mapping with rudimentary JSON templates, these forward-chaining production rules can output JSON-LD according to the RO-Crate 1.1 specification[^2]:
